Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-08-31 supplement.tex
Fix of hyperedge proof

  Let $u$ denote the node in $T$ with maximal distance to the root $r$,
  such that still $C\subseteq\TransVars{u}$.
  Let $C'$ be $C-\chi(u)$.
  If $C'$ is empty than $u$ represents $C$---nothing remains to be shown;
  thus assume, $C' \neq \emptyset$.
  For exactly one of the children $u'$ of $u$,
  $C'\subseteq\TransVars{u'}$, since otherwise for
  some node $v'\in C'$, the subtree of the nodes representing $v'$ would be disconnected (property 2 of Def.~\ref{def:treedecomp}). Now, pick some $v'\in C'$ and some
  $v''\in C-C'$, which must be represented by $u$ or some child $u''$ of $u$. In both cases, there cannot
  be any node in T that represents the edge $\{v',v''\}\subseteq C$, since $v'$ can only be represented 
  by nodes in the subtree of $u'$.
\end{proof}

>>>>

  Assume there is no node in T that represents $C$.

  Let $u$ denote the node in $T$ with maximal distance to the root $r$,
  such that still $C\subseteq\TransVars{u}$.
  Since there is no single node $u$ that represents $C$, this maximal node is unique, since
  if a node $u$, $C\subseteq\TransVars{u}$, has two subtrees that cover $C$, then $u$ must represent $C$ due to property 2 of Def.~\ref{def:treedecomp}.

  Let $C'$ be $C-\chi(u)$.
  $C'$ cannot be empty, since otherwise $u$ represents $C$i.
  For exactly one of the children $u'$ of $u$,
  $C'\subseteq\TransVars{u'}$, since otherwise for
  some node $v'\in C'$, the subtree of the nodes representing $v'$ would be disconnected (property 2 of Def.~\ref{def:treedecomp}). Now, pick some $v'\in C'$ and some
  $v''\in C-C'$, which must be represented by $u$ or some child $u''$ of $u$. In both cases, there cannot
  be any node in T that represents the edge $\{v',v''\}\subseteq C$, since $v'$ can only be represented 
  by nodes in the subtree of $u'$. Contradiction.
\end{proof}
